Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
style edit: added space between Cases

\begin{proof}
	\textbf{Case 1:} First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
	\begin{equation*}
		B^{b_2} \to 0, \quad B^{\eta,b_2} \to 0,
	\end{equation*}
	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that $\lim_{b_2 \to 0} PoA = 1.$

@@

	Hence, for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
	\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon.
	\end{equation*} 
	Since the proof holds for arbitrary $\epsilon > 0$, we obtain:
	\begin{equation*}
	\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0.
	\end{equation*}
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $\lim_{\bar{b}_2 \to \infty}w^{\bar{b}_2}_0 = 0$. Thus, we obtain:
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$$
	and conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$

@@

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.

@@

	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3T/4]$,
	\begin{equation*}
	\begin{split}
	\vert h_u(b_1, t) - h_w(b_1,t) \vert  &=\max \{h_u(b_1, t)-h_w(b_1, t),h_w(b_1, t)-h_u(b_1, t) \}\\
	&\leq \max \{h_u(b_1, 0)-h_w(b_1, 3T/4),h_w(b_1, 0)-h_u(b_1, 3T/4) \} \\
	&\leq \epsilon,
	\end{split}
	\end{equation*}
	and
	$$h_w(b_1,0) \geq 2 - \frac{1}{3} = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, 3T/4) \geq \frac{5}{3}.$$
	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3T/4]$ and $[3T/4, T]$. For all $b_1 \geq b_1^{*,I_1}$, similar to inequality (\ref{eq:I_1_plus_I_2}), we have:
	\begin{equation*}
		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)},
	\end{equation*}
	where
	\begin{IEEEeqnarray*}{rCl}
	I^{b_1}_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
	&= & \epsilon^2 e^{\frac{3\bar{b}_1 T}{2} } \cdot \frac{3}{4}(1-e^{-b_1T})  \nonumber \\	
	& \leq & \kappa_1 \epsilon^2 ,
	\end{IEEEeqnarray*} 	
	in which $\kappa_1 := \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
	\begin{IEEEeqnarray*}{rCl}
		 I^{b_1}_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
		 &=&  9 T e^{2 \bar{b}_1 T} b_1 e^{- \frac{1}{2} b_1 T} \xrightarrow[b_1 \to \infty]{}0.
	\end{IEEEeqnarray*}
	Therefore, there exists $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
	Since the proof holds for arbitrary $\epsilon>0$, and $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} }$ is independent of $b_1$ and $\epsilon$, we conclude that:
	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$

>>>>

\begin{proof}
	\textbf{Case 1:} First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
	\begin{equation*}
		B^{b_2} \to 0, \quad B^{\eta,b_2} \to 0,
	\end{equation*}
	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that $\lim_{b_2 \to 0} PoA = 1.$\\

@@

	Hence, for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
	\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon.
	\end{equation*} 
	Since the proof holds for arbitrary $\epsilon > 0$, we obtain:
	\begin{equation*}
	\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0.
	\end{equation*}
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $\lim_{\bar{b}_2 \to \infty}w^{\bar{b}_2}_0 = 0$. Thus, we obtain:
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$$
	and conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$\\

@@

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.\\

@@

	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3T/4]$,
	\begin{equation*}
	\begin{split}
	\vert h_u(b_1, t) - h_w(b_1,t) \vert  &=\max \{h_u(b_1, t)-h_w(b_1, t),h_w(b_1, t)-h_u(b_1, t) \}\\
	&\leq \max \{h_u(b_1, 0)-h_w(b_1, 3T/4),h_w(b_1, 0)-h_u(b_1, 3T/4) \} \\
	&\leq \epsilon,
	\end{split}
	\end{equation*}
	and
	$$h_w(b_1,0) \geq 2 - \frac{1}{3} = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, 3T/4) \geq \frac{5}{3}.$$
	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3T/4]$ and $[3T/4, T]$. For all $b_1 \geq b_1^{*,I_1}$, similar to inequality (\ref{eq:I_1_plus_I_2}), we have:
	\begin{equation*}
		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)},
	\end{equation*}
	where
	\begin{IEEEeqnarray*}{rCl}
	I^{b_1}_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
	&= & \epsilon^2 e^{\frac{3\bar{b}_1 T}{2} } \cdot \frac{3}{4}(1-e^{-b_1T})  \nonumber \\	
	& \leq & \kappa_1 \epsilon^2 ,
	\end{IEEEeqnarray*} 	
	in which $\kappa_1 := \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
	\begin{IEEEeqnarray*}{rCl}
		 I^{b_1}_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
		 &=&  9 T e^{2 \bar{b}_1 T} b_1 e^{- \frac{1}{2} b_1 T} \xrightarrow[b_1 \to \infty]{}0.
	\end{IEEEeqnarray*}
	Therefore, there exists $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
	Since the proof holds for arbitrary $\epsilon>0$, and $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} }$ is independent of $b_1$ and $\epsilon$, we conclude that:
	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$ \\
